A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\citet{Schilders2008} provides a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric term, to the work of \citet{Odabasioglu_1998} in 1998 which introduced PRIMA - Passive Reduced-order Interconnect Marcromodeling Algorithm. Truncated Balanced Realization \cite{Moore_1981} is one of the MOR methods, published in 1981, it called attention to principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD). Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods published in 1984 and 1987 respectively. In 1990, Asymptotic Waveform Evaluation \cite{Pillage_1990} the first MOR method related to the Krylov was born, this was followed by Pade Via Lanczos \cite{Feldmann_1995} in 1995 and then PRIMA. In this work, upscaling is performed by SVD in the principal component spaces.

>>>>

\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998 which introduced Passive Reduced-order Interconnect Macromodeling Algorithm (PRIMA). Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD). Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods developed published in 1984 and 1987 respectively\red{(I DONT THINK THIS IS ACCURATE ... POD OR KARHUNEN-LOEVE DECOMPOSITION/TRANSFORM ORIGINAL PAPERS ARE FROM 1933-48!)}. The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA. In this work, upscaling is performed by SVD in principal component spaces.
